Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-02-10 paper/main.Rmd
updating figures

# ggpubr::ggscatter(mds,
#                   x = "Dim.1",
#                   y = "Dim.2", 
#                   label = rownames(mds),
#                   size = 1,
#                   repel = TRUE) 
```

@@

#   d = one_harmony_data %>%
#     select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
#     dist()
#   
#   hc = stats::hclust(d,method="complete")
#   plot(hc)
#   groups<-cutree(hc, k=4)
#   
#   all_data_cluster <- cbind(one_harmony_data, groups) %>% 
#     left_join(mds, by = "customer_id") %>% 
#     mutate(groups = as.factor(groups))
# 
# 
# 
# ggpubr::ggscatter(all_data_cluster,
#                   x = "Dim.1",
#                   y = "Dim.2", 
#                   label = rownames(mds),
#                   color = "groups",
#                   size = 1,
#                   repel = TRUE)

@@

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)
library(patchwork)
p1/p2/p3

>>>>

colnames(mds) <- c("Dim.1", "Dim.2")
rownames(mds) <- unique(one_harmony_data$customer_id)
mds <- mds %>%
  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
  select((customer_id)
         , Dim.1, Dim.2)
```

@@

# check transformation and scalar approaches are same

```{r scalar-approach}
set.seed(7777)
all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
set.seed(7777)
sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
  as_tsibble(index = reading_datetime,
             key = customer_id) %>% 
  create_gran("day_week") %>% 
  create_gran("hour_day")

ggpubr::ggscatter(mds,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  size = 1,
                  repel = TRUE)

# clustering as well

d = one_harmony_data %>%
  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
  dist()

hc = stats::hclust(d,method="complete")
plot(hc)
groups<-cutree(hc, k=4)

all_data_cluster <- cbind(one_harmony_data, groups) %>% 
  left_join(mds, by = "customer_id") %>% 
  mutate(groups = as.factor(groups))

ggpubr::ggscatter(all_data_cluster,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  color = "groups",
                  size = 1,
                  repel = TRUE)

@@

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)
library(patchwork)
p1
p2
p3
